Longitudinal Analysis Manuscript: Working Draft

### 2023-04-21 test.tex
cli commit 7

@@

% Header and Footer with logo
\usepackage{lastpage,fancyhdr}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}
% Remove comment for double spacing
% \usepackage{setspace}
% \doublespacing
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[numbers,square,comma]{natbib}
\bibliographystyle{plos2015}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Longitudinal Analysis Manuscript: Working Draft},
  pdfauthor={Samuel W. Hawes; with the Lorem Ipsum Consortium},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Longitudinal Analysis Manuscript: Working
Draft} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
\\
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
Samuel W. Hawes\textsuperscript{1*}, with the Lorem Ipsum
Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Center for Children and Families, Florida International
University, Miami, Florida, United States, 
\bigskip

@@

\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget
porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut
dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id
velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus
finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium
diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut
ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit
pulvinar, volutpat risus.

\section*{Author summary}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget
porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut
dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id
velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus
finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium
diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut
ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit
pulvinar, volutpat risus.

\linenumbersxxxxx

\#title: ``Longitudinal Analaysis Manuscript- Working Draft'' \# format:
\# pdf: \# toc: true \# number-sections: true \# colorlinks: true \#
geometry: \# - top=20mm \# - left=20mm \# docx: default \# prefer-html:
true

xxxxx

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

label\{sec:headings\} The Adolescent Brain Cognitive Development (ABCD)
Study® is the largest long-term investigation of neurodevelopment and
child health in the United States. Conceived and initiated by the
National Institutes of Health (NIH), this landmark prospective
longitudinal study aims to transform our understanding of the genetic
and environmental influences on brain development and their roles in
behavioral and health outcomes in adolescents \citep{volkow2018}. At its
heart, the study is designed to chart the course of human development
across multiple, interacting domains from late childhood to early
adulthood and to identify factors that lead to both positive and
negative developmental outcomes. Central to achieving these goals is the
ABCD Study's® commitment to an open science framework designed to
facilitate access to and sharing of scientific knowledge by espousing
practices that increase openness, integrity, and reproducibility of
scientific research (e.g., public data releases). In this sense, the
ABCD Study® is a collaboration with the larger research community, with
the rich longitudinal nature of the ABCD Study dataset allowing
researchers to perform a variety of analyses of both methodological and
substantive interest. Together, this presents a unique opportunity to
significantly advance our understanding of how a multitude of
biopsychosocial processes emerge and unfold across critical periods of
development.

@@

label\{sec:headings\} There are several important concepts to consider
when conducting longitudinal analyses in a developmental context. These
include different ways of thinking about developmental course, whether
certain periods of development are relatively sensitive or insensitive
to various types of insults or stressors, whether some time periods or
situations inhibit the expression of individual differences due to
extreme environmental pressures, and whether the same behavior
manifested at different times represent the same phenomenon or different
ones. Further, in the case of developmentally focused longitudinal
research, each new measurement occasion not only provides a more
extended portrait of the child's life course (and not just characterize
growth during this period but also assesses the durability/chronicity of
prior effects/consequences) but also brings with it greater
methodological opportunities to exploit the statistical properties of
longitudinal data in the furtherance of critical scientific questions.
That is, we can ask more nuanced questions and make stronger inferences
as our number of time-ordered observations grows, assuming we have
assessed the ``right'' variables and the timings of our observations
comport with the temporal dynamics of the mechanisms of interest.
Appreciation of these and other issues can help to guide the analysis
and interpretation of data and aid translation to clinical and public
health applications.

@@

label\{sec:headings\} \textbf{Defining Features of Longitudinal Data
Analysis.} The hallmark characteristic of longitudinal data analysis is
its application to repeated assessments of the same assessment targets
(e.g., individuals, families) across time. While the primary reason for
collecting longitudinal data is in pursuit of addressing scientific
questions, from a methodological perspective, having multiple
observations over time allows researchers to identify potentially
problematic observations when highly improbable longitudinal patterns
are observed. That is, we can ask more nuanced questions and make
stronger inferences as our number of time-ordered observations grows
assuming we have assessed the ``right'' variables and the timings of our
observations comport with the temporal dynamics of the mechanisms of
interest .

@@

@@

\hypertarget{references}{%
\subsubsection{References}\label{references}}

\renewcommand{\bibsection}{}
\bibliography{references.bib,bibliography.bib}

\nolinenumbers

>>>>

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

@@

% Header and Footer with logo
\usepackage{lastpage,fancyhdr}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}
% Remove comment for double spacing
% \usepackage{setspace}
% \doublespacing
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[numbers,square,comma]{natbib}
\bibliographystyle{plos2015}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Longitudinal Analysis Manuscript: Working Draft},
  pdfauthor={Samuel W. Hawes, PhD.; Andrew K. Littlefield, PhD.; Daniel A. Lopez; Kenneth J. Sher; Wesley K. Thompson; Additional Co-authors1; Additional Co-authors2},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Longitudinal Analysis Manuscript: Working
Draft} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
\\
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
Samuel W. Hawes, PhD.\textsuperscript{1*}, Andrew K. Littlefield,
PhD.\textsuperscript{2}, Daniel A. Lopez\textsuperscript{3}, Kenneth J.
Sher\textsuperscript{4}, Wesley K.
Thompson\textsuperscript{5}, Additional
Co-authors1\textsuperscript{1}, Additional
Co-authors2\textsuperscript{1}
\\
\bigskip
\textbf{1} Center for Children and Families, Florida International
University, Miami, FL, United States, \\ \textbf{2} Psychological
Sciences, Texas Tech University, Lubbock, TX, United
States, \\ \textbf{3} Department of Public Health, University of
Rochester Medical Center, Rochester, NY, United
States, \\ \textbf{4} Psychological Sciences, University of
Missouri, Columbia, MO, United States, \\ \textbf{5} Population
Neuroscience and Genetics Center, Laureate Institute for Brain
Research, Tulsa, OK, United States, 
\bigskip

@@

\section*{Abstract}
The Adolescent Brain Cognitive Development (ABCD) Study presents a
unique opportunity for researchers to investigate developmental
processes in a large, diverse cohort of children and adolescents. Given
the complex nature of the longitudinal data collected in the ABCD Study,
researcher are likely to encounter a myriad of methodological and
analytic considerations and concerns. This review provides a
comprehensive examination of key issues and techniques related to
longitudinal data analysis, specifically focusing on the ABCD Study. The
text discusses model assumptions, common violations (e.g., independent
and identically distributed residuals, \emph{heterogeneous}
\emph{variability}) and their implications for valid inference. The
importance of appropriately modeling covariance structures,
understandings trade-offs between model fit and parsimony, and
challenges related to sample size, attrition, missing data are
highlighted. Consideration is given to the importance of selecting
appropriate statistical models to account for correlations in repeated
measurements and the assumptions underlying these models. The review
also differentiates between linear and non-linear models in the context
of continuous and discrete data, emphasizing various distributional
assumptions and the necessity of choosing appropriate models and
statistical methods. By addressing these complexities, the review seeks
to equip researchers with the necessary knowledge and tools to make
informed decisions as they navigate effectively analyzing and
interpreting data available in the ABCD Study.

\section*{Author summary}
The Adolescent Brain Cognitive Development (ABCD) Study offers valuable
insights into adolescent brain development. Researchers working with
this data face methodological and analytic concerns, including sample
size, attrition, missing data, and measurement. This review addresses
complexities in analyzing longitudinal data, with a focus on statistical
models accounting for correlations in repeated measurements and their
assumptions. We emphasize the importance of choosing appropriate models
and analytic functions based on the data and the specific scientific
question to be addressed. This concise resource aims to help researchers
navigate longitudinal data analysis, make informed methodological
decisions, and enhance the accuracy and reliability of their findings
when working with data from the ABCD Study.

\linenumbers\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\label{sec:headings} The Adolescent Brain Cognitive Development (ABCD)
Study® is the largest long-term investigation of neurodevelopment and
child health in the United States. Conceived and initiated by the
National Institutes of Health (NIH), this landmark prospective
longitudinal study aims to transform our understanding of the genetic
and environmental influences on brain development and their roles in
behavioral and health outcomes in adolescents \citep{volkow2018}. At its
heart, the study is designed to chart the course of human development
across multiple, interacting domains from late childhood to early
adulthood and to identify factors that lead to both positive and
negative developmental outcomes. Central to achieving these goals is the
ABCD Study's® commitment to an open science framework designed to
facilitate access to and sharing of scientific knowledge by espousing
practices that increase openness, integrity, and reproducibility of
scientific research (e.g., public data releases). In this sense, the
ABCD Study® is a collaboration with the larger research community, with
the rich longitudinal nature of the ABCD Study dataset allowing
researchers to perform a variety of analyses of both methodological and
substantive interest. Together, this presents a unique opportunity to
significantly advance our understanding of how a multitude of
biopsychosocial processes emerge and unfold across critical periods of
development.

@@

\label{sec:headings} There are several important concepts to consider
when conducting longitudinal analyses in a developmental context. These
include different ways of thinking about developmental course, whether
certain periods of development are relatively sensitive or insensitive
to various types of insults or stressors, whether some time periods or
situations inhibit the expression of individual differences due to
extreme environmental pressures, and whether the same behavior
manifested at different times represent the same phenomenon or different
ones. Further, in the case of developmentally focused longitudinal
research, each new measurement occasion not only provides a more
extended portrait of the child's life course (and not just characterize
growth during this period but also assesses the durability/chronicity of
prior effects/consequences) but also brings with it greater
methodological opportunities to exploit the statistical properties of
longitudinal data in the furtherance of critical scientific questions.
That is, we can ask more nuanced questions and make stronger inferences
as our number of time-ordered observations grows, assuming we have
assessed the ``right'' variables and the timings of our observations
comport with the temporal dynamics of the mechanisms of interest.
Appreciation of these and other issues can help to guide the analysis
and interpretation of data and aid translation to clinical and public
health applications.

@@

\label{sec:headings} \textbf{Defining Features of Longitudinal Data
Analysis.} The hallmark characteristic of longitudinal data analysis is
its application to repeated assessments of the same assessment targets
(e.g., individuals, families) across time. While the primary reason for
collecting longitudinal data is in pursuit of addressing scientific
questions, from a methodological perspective, having multiple
observations over time allows researchers to identify potentially
problematic observations when highly improbable longitudinal patterns
are observed. That is, we can ask more nuanced questions and make
stronger inferences as our number of time-ordered observations grows
assuming we have assessed the ``right'' variables and the timings of our
observations comport with the temporal dynamics of the mechanisms of
interest .

@@

\hypertarget{general-guidelines-for-this-quarto-template}{%
\section{General guidelines for this Quarto
template}\label{general-guidelines-for-this-quarto-template}}

This template shows how to use PLOS template from
\url{https://plos.org/resources/writing-center/}. Each journal have a
submission guideline page, please refer to it.

\begin{itemize}
\tightlist
\item
  \href{https://journals.plos.org/plosbiology/s/submission-guidelines}{PLOS
  Biology}
\item
  \href{https://journals.plos.org/climate/s/submission-guidelines}{PLOS
  Climate}
\item
  \href{https://journals.plos.org/digitalhealth/s/submission-guidelines}{PLOS
  Digital Health}
\item
  \href{https://journals.plos.org/ploscompbiol/s/submission-guidelines}{PLOS
  Computational Biology}
\item
  \href{https://journals.plos.org/plosgenetics/s/submission-guidelines}{PLOS
  Genetics}
\item
  \href{https://journals.plos.org/globalpublichealth/s/submission-guidelines}{PLOS
  Global Public Health}
\item
  \href{https://journals.plos.org/plosmedicine/s/submission-guidelines}{PLOS
  Medicine}
\item
  \href{https://journals.plos.org/plosntds/s/submission-guidelines}{PLOS
  Neglected Tropical Diseases}
\item
  \href{https://journals.plos.org/plosone/s/submission-guidelines}{PLOS
  ONE}
\item
  \href{https://journals.plos.org/plospathogens/s/submission-guidelines}{PLOS
  Pathogens}
\item
  \href{https://journals.plos.org/sustainabilitytransformation/s/submission-guidelines}{PLOS
  Sustainability and Transformation}
\item
  \href{https://journals.plos.org/water/s/submission-guidelines}{PLOS
  Water}
\end{itemize}

This template file contains some guidelines and recommandation initially
given in \texttt{plos\_latex\_template.tex} that can be found in
\url{https://github.com/quarto-journals/plos/blob/main/style-guide/plos_latex_template.tex}

\hypertarget{metadata}{%
\subsection{Metadata}\label{metadata}}

\hypertarget{about-journal-id-field}{%
\subsubsection{About journal id field}\label{about-journal-id-field}}

This is an identifier for the target journal. It can be derived from
https://plos.org/resources/writing-center/ following submission
guidelines link, the identifier is the part of the URL after
\texttt{https://journals.plos.org/\textless{}id\textgreater{}/s/submission-guidelines}

\begin{longtable}[]{@{}ll@{}}
\toprule\noalign{}
Journal & id \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
PLOS Biology & plosbiology \\
PLOS Climate & climate \\
PLOS Digital Health & digitalhealth \\
PLOS Computational Biology & ploscompbiol \\
PLOS Genetics & plosgenetics \\
PLOS Global Public Health & globalpublichealth \\
PLOS Medicine & plosmedicine \\
PLOS Neglected Tropical Diseases & plosntds \\
PLOS ONE & plosone \\
PLOS Pathogens & plospathogens \\
PLOS Sustainability and Transformation & sustainabilitytransformation \\
PLOS Water & water \\
\end{longtable}

Example :

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{format}\KeywordTok{:}
\AttributeTok{  }\FunctionTok{plos{-}pdf}\KeywordTok{:}
\AttributeTok{    }\FunctionTok{journal}\KeywordTok{:}
\AttributeTok{      }\FunctionTok{id}\KeywordTok{:}\AttributeTok{ water}
\end{Highlighting}
\end{Shaded}

\hypertarget{once-your-paper-is-accepted-for-publication}{%
\subsection{Once your paper is accepted for
publication,}\label{once-your-paper-is-accepted-for-publication}}

Do not include track change in LaTeX file and leave only the final text
of your manuscript. PLOS recommends the use of latexdiff to track
changes during review, as this will help to maintain a clean tex file.
Visit \url{https://www.ctan.org/pkg/latexdiff?lang=en} for info or
contact us at \href{mailto:latex@plos.org}{\nolinkurl{latex@plos.org}}.

\emph{This should not be a problem using Quarto but still a
recommandation from the journal}

There are no restrictions on package use within the LaTeX files except
that no packages listed in the template may be deleted.

Please do not include colors or graphics in the text. Color can be used
to apply background shading to table cells only.

The manuscript LaTeX source should be contained within a single file (do
not use\texttt{\textbackslash{}input},
\texttt{\textbackslash{}externaldocument}, or similar commands).

Please contact \href{mailto:latex@plos.org}{\nolinkurl{latex@plos.org}}
with any questions submission guidelines. For anything Quarto related,
please open an issue in \url{https://github.com/quarto-journals/plos}.
If this is related to the LaTeX template, this could also be a good idea
to contact PLOS directly.

\hypertarget{figures-and-tables}{%
\subsection{Figures and Tables}\label{figures-and-tables}}

Please include tables/figure captions directly after the paragraph where
they are first cited in the text.

\hypertarget{figures}{%
\subsubsection{Figures}\label{figures}}

However, do not include graphics in your manuscript

\begin{itemize}
\tightlist
\item
  Figures should be uploaded separately from your manuscript file.
\item
  Figures generated using LaTeX should be extracted and removed from the
  PDF before submission.
\item
  Figures containing multiple panels/subfigures must be combined into
  one image file before submission.
\end{itemize}

\textbf{This means that, depending on how you create your figure, a
manual post processing will be required.}

For figure citations, please use ``Fig'' instead of ``Figure''. This has
been made the default in this Quarto format:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{crossref}\KeywordTok{:}
\AttributeTok{  }\FunctionTok{fig{-}title}\KeywordTok{:}\AttributeTok{ Fig }
\end{Highlighting}
\end{Shaded}

Also, place figure captions after the first paragraph in which they are
cited.

See PLOS figure guidelines at
\url{https://journals.plos.org/plosone/s/figures} and in your specific
journal guideline.

\hypertarget{tables}{%
\subsubsection{Tables}\label{tables}}

Tables should be cell-based and may not contain:

\begin{itemize}
\tightlist
\item
  spacing/line breaks within cells to alter layout or alignment
\item
  do not nest tabular environments (no tabular environments within
  tabular environments)
\item
  no graphics or colored text (cell background color/shading OK)
\end{itemize}

See PLOS table guidelines at
\url{http://journals.plos.org/plosone/s/tables} and in your specific
journal guideline.

For tables that exceed the width of the text column, use the adjustwidth
environment as illustrated in the example table in text below. If you
are in this case, you'll either need to manually post process the
\texttt{.tex} file and recreate the PDF, or you need to include LaTeX
tables directly.

Also, place tables after the first paragraph in which they are cited.

\hypertarget{equations-math-symbols-subscripts-and-superscripts}{%
\subsection{Equations, math symbols, subscripts, and
superscripts}\label{equations-math-symbols-subscripts-and-superscripts}}

Below are a few tips to help format your equations and other special
characters according to our specifications. For more tips to help reduce
the possibility of formatting errors during conversion, please see our
LaTeX guidelines at http://journals.plos.org/plosone/s/latex

\begin{itemize}
\item
  For inline equations, please be sure to include all portions of an
  equation in the math environment. For example, \texttt{x\$\^{}2\$} is
  incorrect; this should be formatted as \(x^2\) (or \(\mathrm{x}^2\) if
  the romanized font is desired).
\item
  Do not include text that is not math in the math environment. For
  example, \texttt{CO2} should be written as
  \texttt{CO\textbackslash{}textsubscript\{2\}} giving
  CO\textsubscript{2} instead of \texttt{CO\$\_2\$}.
\item
  Please add line breaks to long display equations when possible in
  order to fit size of the column.
\item
  For inline equations, please do not include punctuation (commas, etc)
  within the math environment unless this is part of the equation.
\item
  When adding superscript or subscripts outside of brackets/braces,
  please group using \texttt{\{\}}. For example, change
  \texttt{"{[}U(D,E,\textbackslash{}gamma){]}\^{}2"} to
  \texttt{"\{{[}U(D,E,\textbackslash{}gamma){]}\}\^{}2"}.\\
\item
  Do not use \texttt{\textbackslash{}cal} for caligraphic font. Instead,
  use \texttt{\textbackslash{}mathcal\{\}}
\end{itemize}

\hypertarget{title-and-headings}{%
\subsection{Title and headings}\label{title-and-headings}}

Please use ``sentence case'' for title and headings (capitalize only the
first word in a title (or heading), the first word in a subtitle (or
subheading), and any proper nouns).

PLOS does not support heading levels beyond the 3rd, meaning no 4th
level headings. Header 4 levels \texttt{\#\#\#\#} is used for the
\emph{Supporting information} section

\hypertarget{abstract-and-author-summary}{%
\subsection{Abstract and author
summary}\label{abstract-and-author-summary}}

Abstract must be kept below 300 words.

Author Summary must be kept between 150 and 200 words and first person
must be used.

For PLOS ONE, author summary won't be included as it is not valid for
submission.

\hypertarget{supplementary-information-syntax}{%
\subsection{Supplementary information
syntax}\label{supplementary-information-syntax}}

Use this markdown syntax to create the supplementary information block
with a custom block of class \texttt{.supp}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{::: \{.supp\}}
\FunctionTok{\#\# SI TYPE \{\#id\}}

\NormalTok{First paragraph is a title sentence that will be bold. (required)}

\NormalTok{Optionnaly, add descriptive text after the title of the}
\NormalTok{item. No third paragraph is allowed}
\NormalTok{:::}
\end{Highlighting}
\end{Shaded}

They need to be referenced in text using \texttt{nameref} by using this
syntax \texttt{{[}id{]}(.nameref)} where \texttt{ìd} will be the id used
on the header.

\hypertarget{references}{%
\subsection{References}\label{references}}

Within Quarto, \texttt{natbib} will be used with \texttt{plos2015.bst},
which expect numeric style citation. Use brackets for references, e.g
\texttt{{[}@ref{]}}.

\hypertarget{quarto-features-limitation}{%
\subsection{Quarto features
limitation}\label{quarto-features-limitation}}

Some features are not working with this format in PDF:

\begin{itemize}
\tightlist
\item
  Callouts
\item
  Code highlighting customization (border left, background color)
\end{itemize}

@@

\begin{quote}
\textbf{Following content of this document is from the LaTeX template
content to demo journal style.}
\end{quote}

\hypertarget{introduction-1}{%
\section{Introduction}\label{introduction-1}}

Lorem ipsum dolor sit~\citep{bib1} amet, consectetur adipiscing elit.
Curabitur eget porta erat. Morbi consectetur est vel gravida pretium.
Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam
Eq~\ref{eq-schemeP} sapien tellus, commodo id velit id, eleifend
volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel,
pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor
faucibus id.~\citep{bib2} Nunc convallis sodales ante, ut ullamcorper
est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar,
volutpat risus.

\begin{equation}\protect\hypertarget{eq-schemeP}{}{
\begin{aligned}
\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}}
\end{aligned}
}\label{eq-schemeP}\end{equation}

\hypertarget{materials-and-methods}{%
\section{Materials and methods}\label{materials-and-methods}}

\hypertarget{etiam-eget-sapien-nibh}{%
\subsection{Etiam eget sapien nibh}\label{etiam-eget-sapien-nibh}}

Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod
diam. Proin rutrum vel massa non gravida. Quisque tempor sem et
dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing
elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae
diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat
porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim
semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Place figure captions after the first paragraph in which they are cited.
\begin{figure}[!h]
\caption{{\bf Bold the figure title.}
Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

\hypertarget{results}{%
\section{Results}\label{results}}

Results and Discussion can be combined.

Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat
euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et
dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing
elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae
diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat
porttitor lectus cursus, \nameref{s1-video} vel sagittis arcu lobortis.
Aliquam in enim semper, aliquam massa id, cursus neque. Praesent
faucibus semper libero.

% Place tables after the first paragraph in which they are cited.
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

\hypertarget{lorem-and-ipsum-nunc-blandit-a-tortor}{%
\subsection{\texorpdfstring{\textbf{LOREM}~and \textbf{IPSUM}~nunc
blandit a
tortor}{LOREM~and IPSUM~nunc blandit a tortor}}\label{lorem-and-ipsum-nunc-blandit-a-tortor}}

\hypertarget{rd-level-heading}{%
\subsubsection{3rd level heading}\label{rd-level-heading}}
